Performance Evaluation of Big Data Processing Strategies for Neuroimaging

### 2018-12-09 paper.tex
More methods added to paper. fixed bug in makespan extraction code

% Dedicated Compute nodes with SLURM
% Lustre server

\begin{table}
\centering
\begin{tabular}{c|c}
$\delta/\gamma$ & $\Delta/\Gamma$\\
\hline
50~MB/s         & 5~MB/s
\end{tabular}
\label{table:infrastructure}
\caption{Bandwidth thresholds on the target cluster}
\end{table}

@@

% BigBrain
% Some BIDS dataset for fmriprep

@@

% Incrementation (avoid cache effects in binarization)

>>>>

All experiments were executed on the Dell Zenith cluster~\cite{dellHPC} running 
SLURM. For the 
Spark experiments, a Spark cluster was started atop our SLURM allocation. We
had access to 16 dedicated nodes. Each compute node ran on RHEL 7.4, was 
equipped with 40 Intel Xeon Gold 6148 2.4GHz CPUs and had
187GB of memory, 94GB of tmpfs and a Dell 120GB M.2 SATA SSD as local disk. 
A 698TB Lustre server is accessible on each node through a 100Gb/s Infiniband
network. The apparent bandwidth of the local disk was found to be 1480MB/S, 
whereas Lustre's bandwidth was found to be at 401.49MB/S.
% Dedicated Compute nodes with SLURM
% Lustre server

\begin{table}
\centering
\begin{tabular}{c|c}
$\delta/\gamma$ & $\Delta/\Gamma$\\
\hline
164.5~MB/s         & 3.2~MB/s
\end{tabular}
\label{table:infrastructure}
\caption{Bandwidth thresholds on the target cluster using 15 worker nodes and a
         maximum of 9 CPUs on each node.}
\end{table}

@@

% BigBrain
% Some BIDS dataset for fmriprep
For our experiments, BigBrain~\cite{bigbrain} a 75GB 40$\mu$m isotropic 
histological image of a 65-year-old male's brain. The BigBrain was selected due 
to being the only one of its kind, as there does not yet exist a 
higher-resolution image of a human brain. Moreover, there currently exists a 
lack of standardized tools for processing the BigBrain as a consequence 
of its size. To examine the effects processing BigBrain has on the Big Data 
strategies, we partitioned the full 3845X3015X3470 voxel image into 30 (5X3X2)
chunks, 125 (5X5X5) chunks and 750 (5X15X10) chunks. Additionally, the full 
image was also split in half (769X603X347 voxels) and the half image was 
partitioned into 125 chunks.

Processing large images are only considered to be part of the BigData problem 
in neuroscience. The other problem is processing large MRI datasets, that is,
datasets consisting of many small brain images belonging to various different 
subjects. Although we have not explored explicitly the processing of large MRI
datasets, the 75GB BigBrain is within the size ballpark~\cite{VanHorn2014} of 
what a large MRI dataset would be today.

As it is possible that both small and large data may need to be processed using
the same pipeline \todo{explain pipelines in intro if not done already}, we 
wanted to determine the effects of the data management strategies on small 
data as well. For this, we selected a 12MB T1W image belonging to subject 1 of 
the ds000001 dataset version 6 ~\cite{openneuro}. In order to be able to split 
it into 125 chunks, it was necessary to zero-pad the image to the dimensions
165X200X200 voxels, which subsequently increased the total image size to 13M.

@@

% Incrementation (avoid cache effects in binarization)
In order to investigate how the different strategies impact processing, we 
selected a simple incrementation pipeline that consisted exclusively of map 
stages. To would allow us to create experiments to tweak data locality, 
in-memory computing and lazy evaluation easily. Incrementation was selected 
over other applications, such as binarization, as it ensured that a new image
was created at each step (i.e. no caching effects within the executing 
application). Each partitioned chunk was incremented by 1, in parallel, by
the processing engines. The incremented chunks would be either 
maintained in-memory (Spark only) or saved to either tmpfs, local disk or 
Lustre (Spark and Nipype). Should more than a single iteration be requested, 
the increment chunks would be incremented again and saved to the same storage. 
This would repeat until the number of requested iterations had elapsed. In all 
conditions, the first input chunks would be reads from Lustre and the final 
output chunks would be saved to Lustre. We chose to to perform our initial 
reads and final writes on Lustre as a multi-tenant clusters' compute node's 
local storage, if 
available, is generally temporary and only available for the duration of the 
allocation.

For our first and second experiment\todo{better split into two paragraphs}, we wanted to determine the effects of in-memory 
processing on increasing data size and task duration. In other words, the 125 
chunk BigBrain 
image was increment 1, 10 and 100 times, such that the total processed data 
size increased from 75GB, at 1 iteration, to 7500GB at 100 iterations. In order
to validate the model, the D/C was varied to fall in different regions of 
Equation~\ref{eq:page-cache-inequality}. The D/C selected were 256, 178.6, 80 
and 1.9MB/s\todo{present this as a table?}. 80 and 1.9MB/s satisfied the 
inequality for local disk, whereas only 1.9MB/s satisfied the inequality for 
Lustre. These D/C ratios were applied to each iteration experiment, such that 
we were able to get both the effect of increasing the total amount of data, in 
addition to, increasing the task duration for a given data size.

As a third incrementation experiment, we were interested in the effects of 
chunk size on in-memory computing. Naturally, greater chunk size signifies 
a decrease in parallelization, however, it also means an increase in sequential
I/O. For this experiment we incremented the 30, 125 and 750 chunk complete
BigBrain image. The amount of parallelization for 30 chunks was 2 cores/node, 
whereas it was 9 cores/node for 125 chunks and 25 cores/node for 750 chunks. 
While Spark attempted to load-balance the data, it used up only 25 of the 40 
cores for 750 chunks. In contrast, Nipype tried to use up as many cores as 
possible. To ensure both engines were processing the same amount of data 
concurrently, we fixed the amount of cores used to 25.
Unlike the previous experiment, the D/C ratio was kept static at 174.4MB/s, 
however, this ratio ensured that different regions of the inequality were 
reached depending on amount of parallelization. A ratio of 174.4 MB/s satified
the inequality for local disk at 30 chunks. All other ratios did not satisfy 
the inequality for Lustre and local disk. Unfortunately, 30 chunks could no be 
processed using in-memory Spark as its individual chunk size of 3GB exceeded 
the 2GB partition size limit imposed by Spark.

For our fourth and final incrementation experiment, we investigated the effects 
of the strategies on different image sizes. We selected the 75GB BigBrain, the
38GB half BigBrain and the 13M T1W MRI image for this experiment. The number of
chunks was fixed at 125. Similarly to the previous experiment, the total 
sequential compute time was fixed, however, due to varying size in total data 
processed, the D/C ratio varied. Once again, we ensure that the D/C ratio fell
in multiple different regions of the inequality.
